An Embedding Framework for Consistent Polyhedral Surrogates

### 2019-05-22 neurips-19/poly-embed.tex
cost-sensitive example

\section{Consistency via Separated Links}
\label{sec:separated-links}

@@

\subsection{New surrogates for cost-sensitive classification}
\raf{DKR construction applied to this.}
\raf{hexagon as an illustration of how easy it is to generate new ones in low dimensions}

>>>>

\section{Consistency via Separated Links}
\label{sec:calibration}

@@

\subsection{New surrogates for cost-sensitive classification}

The construction given in Theorem~\ref{thm:discrete-loss-poly-embeddable}, together with the calibrated link construction in Section~\ref{sec:calibration}, can generate consistent convex surrogates for arbitrary discrete losses.
For example, consider cost-sensitive classification; given an arbitrary loss matrix $C \in \reals^{n\times n}_+$ describing the loss $\ell_j(i) = C_{ij}$ of predicting label $i$ when the true label is $j$, we construct a convex surrogate based on the convex conjugate of $-\risk{\ell}$.
While of course several surrogates are known for this problem~\raf{Jessie, could you cite \url{http://proceedings.mlr.press/v28/avilapires13.pdf} here}, they typically work in $n$ dimensions.
one advantage of our embedding framework is the ability to construct lower-dimensional surrogates when costs have certain geometric interpretations.
For example, if $v_1,\ldots,v_n \in \reals^k$ are on the unit sphere and $C_{ij} = \inprod{v_i}{v_j}$, we can simply take $L_j(u) = $\raf{aaaand Noah woke up}
